Language-Based Security for Low-Level MPC

### 2024-09-03 ppdp24/slides.tex
checkpoint

  Existing HLLs rely on low-level MPC protocols with correctness
  assumed.
  \begin{itemize}
  \item Low-level protocols possess distinct features, e.g., probabilistic sampling.
  \item Existing proof techniques manual, error prone, complex security model.
  \end{itemize}
  Our contributions:
  \begin{itemize}
  \item Language design for low-level protocol definitions.
  \item (Re)formulation of security mode as \cemph{hyperproperties} (e.g., noninterference).
  \item Automated proof techniques.
  \end{itemize}

@@

  \begin{exampleblock}{Example: 3-Party xor}
  $$
  \idealf(\sx{1}{1},\sx{2}{2},\sx{3}{3}) =
  \sx{1}{1}\ \exor\ \sx{2}{2}\ \exor\ \sx{3}{3}
  $$
  Suppose in a run of $\prog$ the output of $\prog$ is 1 and $C = \{ 3 \}$ and
  the adversary knows $\sx{3}{3} = 0$, and therefore either:
  $$
  \sx{1}{1} = 0 \wedge \sx{2}{2} = 1
  $$
  or:
  $$
  \sx{1}{1} = 1 \wedge \sx{2}{2} = 0
  $$
  with \cemph{equal probability of .5}. \cemph{Adversarial views from the run of $\prog$ should not
    allow the adversary better guesses.}
  \end{exampleblock}

@@

  \begin{itemize}
  \item Messages $\mx{ss1}$ through $\mx{ss3}$ are \emph{not} probabilistically independent of inputs, but ...
  \item They \emph{are} independent of secrets conditioned on the output!
  \end{itemize}

@@

>>>>

  Existing HLLs rely on low-level MPC protocols with correctness
  assumed.
  \begin{itemize}
  \item Low-level protocols possess distinct features, e.g., probabilistic sampling.
  \item Existing proof techniques manual, error prone, complex security model.
  \end{itemize}
  Our contributions:
  \begin{itemize}
  \item Language design for low-level protocol definitions.
  \item (Re)formulation of security mode as \cemph{hyperproperties} (e.g., noninterference).
  \item Semi-automated proof techniques.
    \begin{itemize}
    \item Automatically verify small program components, manually combine for whole-program proofs. 
    \end{itemize}
  \end{itemize}

@@

  \begin{exampleblock}{Example: 3-Party xor in $\mathbb{F}_2$}
  $$
  \idealf(\sx{1}{1},\sx{2}{2},\sx{3}{3}) =
  \sx{1}{1}\ \exor\ \sx{2}{2}\ \exor\ \sx{3}{3}
  $$
  Suppose in a run of $\prog$ the output of $\prog$ is 1 and $C = \{ 3 \}$ and
  the adversary knows $\sx{3}{3} = 0$, and therefore either:
  $$
  \sx{1}{1} = 0 \wedge \sx{2}{2} = 1
  $$
  or:
  $$
  \sx{1}{1} = 1 \wedge \sx{2}{2} = 0
  $$
  with \cemph{equal probability of .5}. \cemph{Adversarial views from the run of $\prog$ should not
    allow the adversary better guesses.}
  \end{exampleblock}

@@

  \begin{itemize}
  \item Messages $\mx{ss1}$ through $\mx{ss3}$ are \cemph{not probabilistically independent of inputs}, but ...
  \item They \emph{are} \cemph{independent of secrets conditioned on the output}!
  \end{itemize}

@@

\begin{frame}{Prelude and Component Definitions}

  The Prelude language allows modular definition of Overture protocol components.
  \begin{itemize}
  \item Function definitions, function calls, structured data.
  \item A \emph{staged} language that generates a complete Overture protocol
    as a side effect.
  \end{itemize}
  In addition to programmer convenience, Prelude supports verification:
  \begin{itemize}
  \item Prelude functions define Overture (sub)protocols that can be automatically verified.
  \item Large protocols can be verified manually by composing function properties. 
  \end{itemize}

  \begin{exampleblock}{Example: Summing Shares}
    $$
    \ttt{sum}(x,y,z,i) \{ \mx{z}{i} := \elab{\mesg{x} \fplus \mesg{y}}{i} \} 
    $$
  \end{exampleblock}
\end{frame}
